A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-01-09 manuscript/main.tex
Thu Jan  9 04:57:33 PM EST 2025

\subsection{Implementation}
Python
Pennylane
Pennylane Qiskit
Pennylane Qulacs
Qiskit
SciPy
Scikit-learn

@@

Error mitigation using
MITIQ (delete because this is useless for the Qiskit stuff... try level 2 for ZNE...)

@@

\subsection{Classical Data Analysis}

@@

>>>>

\subsection{Implementation}
Python
Pennylane\cite{bergholm_pennylane_2022}
Pennylane Qiskit\cite{javadi-abhari_quantum_2024}
Pennylane Qulacs\cite{suzuki_qulacs_2021}
Qiskit\cite{javadi-abhari_quantum_2024}
SciPy Minimize \cite{virtanen_scipy_2020}
Scikit-learn\cite{pedregosa_scikit-learn_2011}

``All HF calculations were performed in the Psi4 \cite{parrish_psi4_2017} program. The MP2 and coupled-cluster calculations were performed using the Psi4Numpy \cite{smith_psi4numpy_2018} spin-factored CCSD implementation. \cite{stanton_direct_1991}''

@@

Error mitigation using
TREX \cite{van_den_berg_model-free_2022}

@@

@@

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/linear_error_mitigation.png}
		\caption{}
		\label{fig:linear_error_mitigation}
	\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../images/Function_Fitting/quadratic_error_mitigation.png}
		\caption{}
		\label{fig:linear_error_mitigation}
	\end{subfigure}	
	\caption{}
	\label{fig:functionfitting_errormitigation}	
\end{figure}
